Missing The Point

### 2020-09-24 Manuscript.Rmd
Interpret rhat curves

# sim results plotting function
generic_plot <- function(v, name, ...){
  results %>%
    mutate(
      p = factor(p, levels = c(0.05, 0.5, 0.95), labels = c("5%", "50%", "95%")),
      mech = factor(mech, levels = c("MCAR", "MAR", "MNAR"))
      ) %>% 
  ggplot(aes(
    x=.data[["it"]], 
    y=.data[[v]], 
    color = .data[["p"]], 
    shape = .data[["mech"]], 
    linetype = .data[["mech"]]
    )) +
  #geom_point(na.rm = TRUE) +
  geom_line(na.rm = TRUE) +
  labs(
    x = "Number of iterations",
    y = name,
    color = "Incomplete \n cases", 
    shape = "Missingness \n mechanism", 
    linetype = "Missingness \n mechanism") +
  theme_classic() + 
  scale_color_manual(values = c(
    #"#009E73", #green
    "#56B4E9", #blue
    #"#E69F00", #orange
    "#F0E442", #yellow
    "#D55E00"  #red
  ))
  # scale_color_manual(values = c(
  #   # '#228833', #green
  #   # '#66CCEE', #blue
  #   '#CCBB44', #yellow
  #   '#EE6677',  #red~ish
  #   '#AA3377'  #maroon
  #   ))
}
```

@@

```{r echo=FALSE}
generic_plot(v="est", name = "Regression estimate") + 
  list(geom_hline(yintercept = 1, color = "grey"))

@@

```{r echo=FALSE}
generic_plot(v="cov", name = "Coverage rate") + 
  list(geom_hline(yintercept = 0.95, color = "grey"))

@@

>>>>

# sim results plotting function
generic_plot <- function(v, name, ...){
  results %>%
    mutate(
      p = factor(p, levels = c(0.05, 0.5, 0.95), labels = c("5%", "50%", "95%")),
      mech = factor(mech, levels = c("MCAR", "MAR", "MNAR"))
      ) %>% 
  ggplot(aes(
    x=.data[["it"]], 
    y=.data[[v]], 
    color = .data[["p"]], 
    shape = .data[["mech"]], 
    linetype = .data[["mech"]]
    )) +
  geom_line(na.rm = TRUE) +
  labs(
    x = "Number of iterations",
    y = name,
    color = "Incomplete \n cases", 
    shape = "Missingness \n mechanism", 
    linetype = "Missingness \n mechanism") +
  theme_classic() + 
  scale_color_manual(values = c(
    #"#009E73", #green
    "#56B4E9", #blue
    #"#E69F00", #orange
    "#F0E442", #yellow
    "#D55E00"  #red
  ))
  # scale_color_manual(values = c(
  #   # '#228833', #green
  #   # '#66CCEE', #blue
  #   '#CCBB44', #yellow
  #   '#EE6677',  #red~ish
  #   '#AA3377'  #maroon
  #   ))
}
```

@@

```{r echo=FALSE}
generic_plot(v = "est", name = "Regression estimate") + 
  list(geom_hline(yintercept = 1, color = "grey"))

@@

```{r echo=FALSE}
generic_plot( v ="cov", name = "Coverage rate") + 
  list(geom_hline(yintercept = 0.95, color = "grey"))

# generic_plot( v ="cov", name = "Coverage rate") + 
#   list(geom_hline(yintercept = 0.95, color = "grey")) +
#   ylim(0.85, 1)

@@

These rhat plots all show some initialization before the fifth iteration: is rhat usefull before that??
